### 2014-05-14 doc/thesis/review.tex
Adding some figures to the section about gradual typing

Unfortunately, there is no common formalization for optional type
systems, so each language ends up implementing its optional type
system on its own way.
Strongtalk, Dart, and TypeScript provide an informal description of
their optional type systems rather than a formal one.
In the next section we shall see that we can use some aspects
of gradual typing \citep{siek2006gradual,siek2007objects} to
formalize optional type systems.

@@

@@

@@

@@

>>>>

Unfortunately, there is no common formalization for optional type
systems, so each language ends up implementing its optional type
system on its own way.
Strongtalk, Dart, and TypeScript provide an informal description of
their optional type systems rather than a formal one.
In the next section we shall see that we can use some features
of gradual typing \citep{siek2006gradual,siek2007objects} to
formalize optional type systems.

@@

\begin{figure}[!ht]
\textbf{Syntax of the gradually-typed lambda calculus}\\
\dstart
$$
\begin{array}{rlr}
T ::= & & \emph{types}\\
& \;\; \Number & \emph{base type number}\\
& | \; \String & \emph{base type string}\\
& | \; ? & \emph{dynamic type}\\
& | \; T \rightarrow T & \emph{function types}\\
e ::= & & \emph{expressions}\\
& \;\; c & \emph{constants}\\
& | \; x & \emph{variables}\\
& | \; \lambda x{:}T{.}e & \emph{abstractions}\\
& | \; e_{1} e_{2} & \emph{application}
\end{array}
$$
\dend
\caption{Syntax of the gradually-typed lambda calculus}
\label{fig:gtlc}
\end{figure}

@@

\begin{figure}[!ht]
\textbf{Type consistency}\\
\dstart
$$
\begin{matrix}
\Number \sim \Number \mylabel{C-NUM} \;\;\; \String \sim \String \mylabel{C-STR}
\\ \\
T \sim \;? \mylabel{C-ANY1} \;\;\; ? \sim T \mylabel{C-ANY2}
\\ \\
\dfrac{T_{3} \sim T_{1} \;\;\; T_{2} \sim T_{4}}
      {T_{1} \rightarrow T_{2} \sim T_{3} \rightarrow T_{4}} \mylabel{C-FUN}
\end{matrix}
$$
\dend
\caption{The consistency relation}
\label{fig:consistency}
\end{figure}

@@

\begin{figure}[!ht]
\textbf{Gradual Type System}\\
\dstart
$$
\begin{matrix}
\dfrac{\env(x) = T}
      {\env \vdash x:T} \mylabel{T-VAR}
\;\;\;
\dfrac{type(c) = T}
      {\env \vdash c:T} \mylabel{T-CONST}
\\ \\
\dfrac{\env, x:T_{1} \vdash e:T_{2}}
      {\env \vdash \lambda x:T_{1}.e:T_{1} \rightarrow T_{2}} \mylabel{T-ABS}
\;\;\;
\dfrac{\env \vdash e_{1}:\;? \;\;\;
       \env \vdash e_{2}:T}
      {\env \vdash e_{1} e_{2}:\;?} \mylabel{T-APP1}
\\ \\
\dfrac{\env \vdash e_{1}:T_{1} \rightarrow T_{2} \;\;\;
       \env \vdash e_{2}:T_{3} \;\;\;
       T_{3} \sim T_{1}}
      {\env \vdash e_{1} e_{2}:T_{2}} \mylabel{T-APP2}
\end{matrix}
$$
\dend
\caption{Typing rules of gradually-typed lambda calculus}
\label{fig:gts}
\end{figure}

@@

\begin{figure}[!ht]
\textbf{Consistent-Subtyping}\\
\dstart
$$
\begin{matrix}
\Number \lesssim \Number \mylabel{C-NUM} \;\;\; \String \lesssim \String \mylabel{C-STR}
\\ \\
T \lesssim \;? \mylabel{C-ANY1} \;\;\; ? \lesssim T \mylabel{C-ANY2}
\\ \\
\dfrac{T_{3} \lesssim T_{1} \;\;\; T_{2} \lesssim T_{4}}
      {T_{1} \rightarrow T_{2} \sim T_{3} \rightarrow T_{4}} \mylabel{C-FUN}
\;\;\;
\dfrac{\forall i \in 1..n \;\;\; T_{i} \lesssim T_{i}'}
      {[l_{i}:T_{i}^{\;i\in1..n+m}] \lesssim [l_{i}:T_{i}'^{\;i\in1..n}]} \mylabel{C-OBJ}
\end{matrix}
$$
\dend
\caption{The consistent-subtyping relation}
\label{fig:consistent-subtyping}
\end{figure}
